\section*{Agent and Object description}
In our project we (team pjt) use following agent and objects:
\begin{enumerate}
    \item Agents per pakery:
        \begin{enumerate}
            \item [-] Scheduler $\rightarrow$ Is needed to schedule orders. It checks whether the order can be processed - so is there enough time to prepare the order
            under given circumstances?
            \item [-] OrderProcessing $\rightarrow$ The Order Procesing agent receives an order from the client, distributes the order to all agents, talks to the scheduler
            to verify whether order is feasible and gives the customer a hint whether its order can be processed or not.
            \item [-] DoughManager $\rightarrow$ He manages the kneading machines and preparation tables for one bakery. He ensures that its kneading machines and preparation
            tables are synchron with the time keeper, checks whether current kneaded and prepared products are finished and sends kneaded and prepared orders to proofer.
            \item [-] Proofer $\rightarrow$ The proofer proofs the orders and sends them to the bakery.
        \end{enumerate}
    \item Objects :
        \begin{enumerate}
            \item [-] BakedGood $\rightarrow$ Name of product and the amount of it for one order within DoughPreparationStage.
            \item [-] CurrentProcessedProduct $\rightarrow$ An object which describes the current kneaded product. In other
            context it is used to describe the current prepared product. Moreover it is used to remeber already kneaded
            and prepared products.
            \item [-] KneadingPreparingMachine $\rightarrow$ Describes kneading and preparing machines. It stores the current
            kneaded / prepared order , the progress of preparing / kneading and it checks whether the preparation has finished
            \item [-] Order $\rightarrow$ An object for Scheduler and OrderProcessing Agent. It stores information as customer
            agent id, order day, order hour, delivery day and delivery hour.
            \item [-] OrderDoughPrep $\rightarrow$ An object for storing received orders from Scheduler.
            \item [-] Product $\rightarrow$ An object which stores information on the product (preparation time,
            salesPrice, boxingTemp, guid)
        \end{enumerate}
\end{enumerate}